The impact of cosmic variance on simulating weak lensing surveys

### 2014-10-22 Writeup/paper_v3.tex
clean up discussion related to equations 3 and 4, and remove conversation

The parametric redshift distributions that we use are
\begin{equation}\label{E:pz1}
 p_1(z) \propto z^{a-1}\exp\left[{-z/z_1}\right]
\end{equation}
and 
\begin{equation}\label{E:pz2}
 %p_2(z) \propto z^2\exp{\left[-\left(\frac{z}{z_0}\right)^{1.5}\right]},
 p_2(z) \propto z^{b-1}\exp\left( -\frac{1}{2}\left( \frac{z}{z_2} \right)^2\right)
\end{equation}
%the latter of which was first presented by \cite{Redshift_modelling}.
Here $a$, $b$, $z_1$ and
$z_2$ are free parameters that are to be determined.  The
normalization constants depend not only on the parameters but also on
the lower and the upper limit of the redshifts considered, where we
fix the normalization to ensure that the predicted number of galaxies
in the range used ($0.3<z<1.25$) is equal to the actual number. 
Fig.~\ref{fig:redshift_fluxlimited} shows the photometric redshift
histogram together with the best-fitting parametric distributions.

We compare our fits to the fits made by \cite{2004ApJ...617..765C} for 
the DEEP2 survey. Interpolating their results for the $18<I_\text{AB}<23$
and $18<I_\text{AB}<24$ samples, we obtain that the redshift distributions 
as

\begin{equation}
 \label{E;pz3}
 p_3(z) \propto z^2 \exp{[-z/0.262]}
\end{equation}
and 
\begin{equation}
 \label{E;pz4}
 p_4(z) \propto z^2 \exp{[-(z/0.361)^{1.2}]}
\end{equation}

which are also plotted in Fig.~\ref{fig:redshift_fluxlimited}.

\rachel{New suggestion re: 2nd redshift distribution: it just looks so
  bad, I worry that this functional form is simply wrong 
  and we should use something newer that has been shown to work with
  modern redshift surveys.  Let me suggest something you can
  do as an immediate sanity check.   Look at
  \cite{2004ApJ...617..765C} table 4, which gives parametrized fits to
  the redshift distribution from DEEP2 for samples binned by
  $R_\text{AB}$ and $I_\text{AB}$.  Use the results for the
  $18<I_\text{AB}<23$ bin and the $18<I_\text{AB}<24$ bin,
  interpolating linearly between them since your sample is limited at
  $23.5$.  Their results suggest that either $z^2 \exp{[-z/0.262]}$ or
  $z^2 \exp{[-(z/0.361)^{1.2}]}$ should be decent descriptions of your sample.  Just as a quick
  sanity check can you please plot those  distributions (appropriately
  normalized) on top of what you have in the top panel of figure 1,
  and see how they look?  If they look OK, then I would be inclined to
  completely eliminate the 2nd distribution, and just use the 1st one
  that you're fitting and one of the ones from Coil as your way of
  checking overdensities and underdensities.
} \arun{The functional forms with the parameters in  \cite{2004ApJ...617..765C} agree well with the histogram and our models.}

>>>>

The parametric redshift distributions that we use are
\begin{equation}\label{E:pz1}
 p_1(z) \propto z^{a-1}\exp\left[{-z/z_1}\right]
\end{equation}
and 
\begin{equation}\label{E:pz2}
 %p_2(z) \propto z^2\exp{\left[-\left(\frac{z}{z_0}\right)^{1.5}\right]},
 p_2(z) \propto z^{b-1}\exp\left[ -\frac{1}{2}\left( \frac{z}{z_2} \right)^2\right]
\end{equation}
%the latter of which was first presented by \cite{Redshift_modelling}.
Here $a$, $b$, $z_1$ and
$z_2$ are free parameters that are to be determined.  The
normalization constants depend not only on the parameters but also on
the lower and the upper limit of the redshifts considered, where we
fix the normalization to ensure that the predicted number of galaxies
in the range used ($0.3<z<1.25$) is equal to the actual number. 
Fig.~\ref{fig:redshift_fluxlimited} shows the photometric redshift
histogram together with the best-fitting parametric distributions.

We compare our fits to the fits made by \cite{2004ApJ...617..765C} using 
the DEEP2 galaxy redshift survey. Interpolating between their results for the $18<I_\text{AB}<23$
and $18<I_\text{AB}<24$ samples to our own limiting magnitude (and assuming equivalence of our $I$ bands), we obtain the following redshift distributions:
\begin{equation}
 \label{E;pz3}
 p_3(z) \propto z^2 \exp{[-z/0.262]}
\end{equation}
and 
\begin{equation}
 \label{E;pz4}
 p_4(z) \propto z^2 \exp{[-(z/0.361)^{1.2}]}
\end{equation}
which are also plotted in Fig.~\ref{fig:redshift_fluxlimited}.  
Note that $p_3(z)$ is a special case of $p_1(z)$ with $a=3$ and
$z_1=0.262$; these parameter values are within the $1\sigma$ allowed
regions for our fits to Eq.~\ref{E:pz1}.  Visually, these
distributions appear quite similar to our own fits carried out here, which is
reassuring given the use of different survey data and functional forms.
